\documentclass[12pt,a4paper]{moderncv}
\moderncvtheme[blue]{classic}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}

\usepackage[top=1.1cm, bottom=1.1cm, left=15mm, right=15mm]{geometry}
\recomputelengths


% Largeur de la colonne pour les dates
\setlength{\hintscolumnwidth}{2.5cm}

\firstname{Alban}
\familyname{Dericbourg}
\title{Software engineer\newline{}\small{Graduated from Arts et Métiers ParisTech (ENSAM) and Supélec}}
\address{38 rue Richard Lenoir}{75011 Paris}
\email{alban@dericbourg.net}
\homepage{http://www.dericbourg.net}
\mobile{(+33) 6 61 24 71 74}
\extrainfo{32 years-old}
\begin{document}
\maketitle

\section{Experience}
\cventry{Since jan. 2016}{Criteo}{}{Paris}{}{
  \begin{itemize}
    \item \emph{Criteo Dynamic Email}: e-mail retargeting (jan. 2016 - feb. 2017)
    \begin{itemize}
      \item Software engineer in a distributed team (Paris, Bucharest, Grenoble)
      \item OKR owner: industrialize e-mail templating
    \end{itemize}
    \item Scalability team (since mar. 2017)
    \begin{itemize}
      \item Team in charge of SDKs for low-latency applications. My work is focused on service discovery and application metrics
      \item OKR owner: migrate from an in-house metric aggrgation system to Prometheus, define and deploy a unique application identifier used in observability services
      \item Informal Java / Scala support: entry-point for Scala topics, version upgrade Criteo-wide on my own initiative
    \end{itemize}
  \end{itemize}
  \emph{Environnement : Java 7/8, Scala, Finatra, Spring, SQL Server, Mesos, C\#, Prometheus, Consul}
}

\cventry{Apr. 2015 -- nov. 2015}{Spideo}{}{Paris}{}{
  Profile-based and content-based recommendation of video content (VoD and TV).
  \begin{itemize}
    \item Tech lead
    \item Development and maintenance of APIs consumed by content providers
    \item Set-up of configuration management and automatic deployment
  \end{itemize}
  \emph{Environment : Java 7/8, Scala, Jersey, Guice, MongoDB, Cassandra, Elasticsearch, Kafka, Ansible, AWS, Git, Kanban}
}

\cventry{Oct. 2014 -- apr. 2015}{RATP}{service for Ippon Technologies}{Noisy-le-Grand (93)}{}{
  \begin{itemize}
    \item New software factory
    \begin{itemize}
      \item Requirements study and implementation
      \item Process definition with end-users (developers and project managers)
    \end{itemize}
    \item Development and maintenance of "white application" (Play \emph{templates})
  \end{itemize}
  \emph{Environment : Git, Jenkins, Sonar, Artifactory, Redmine, Gitlab, Android, Play Framework}
}

\cventry{Jul. 2013 -- oct. 2014}{Darty}{service for Ippon Technologies}{Bagnolet (93)}{}{
  \begin{itemize}%
    \item Micro-services refactoring of the information system
    \begin{itemize}
      \item "Availability" component (Darty's ability to deliver goods to customers) with high stress constraints
      \item "OMS" component (order management system)
    \end{itemize}
    \item Monitoring set-up (logs and application metrics)
  \end{itemize}
  \emph{Environment : Dropwizard, Guice, Java 7, FreeMarker, Guava, Jackson, Jersey, JDBI, Maven, Gradle, DB2, YourKit, Google Charts, AngularJS, Grunt, Bower, Liquibase, Elasticsearch, Logstash, Kibana, Graphite}
}

\cventry{Dec. 2012 -- jul. 2013}{Digiplug}{service for Ippon Technologies}{Paris}{}{
  Application to manage releases (clips, albums\dots) from UMGI catalog.\newline{}
  \emph{Environment : Spring, Hibernate, Java 6, Maven, Jetty, JUnit, EasyMock, Oracle, framework Java propriétaire}
}

\cventry{2009 -- 2012}{Archives Nationales}{service for Klee Group}{Le Plessis Robinson (92)}{}{
  Archive management application (after a one-shot relocation helper application).
  \begin{itemize}
    \item Development of business modules
    \item System administration of virtual machines (development and integration)
    \item Continuous integration management
    \item Industrialization (code generators, common tasks automation)
  \end{itemize}
  \emph{Environment : Java 6 (proprietary framework), Tomcat / JBoss, Maven 2, Solr, Oracle, Subversion, .Net 3.5 compact on mobile devices}
}

\cventry{2011 -- 2012}{Vinci PARK}{service for Klee Group}{Le Plessis Robinson (92)}{}{
  Customer and accounting management application.
  \begin{itemize}
    \item Data modeling
    \item Technical quality manager (developer support, code review, metrics and test framework set-up)
    \item Took part in technical architecture set-up (Windows cluster, SQL Server cluster, Hyper-V / Virtual Machine Manager)
  \end{itemize}
  \emph{Environment : .Net 4 (framework propriétaire), SQL Server 2008R2, Visual Studio 2010, PowerDesigner, CruiseControl, TFS, MsTest}
}

\cventry{Feb. -- apr. 2012}{Spark Archives}{software editor, Klee Group subsidiary}{Le Plessis Robinson (92)}{}{
  Archive management sofware.
  \begin{itemize}
    \item Design and implementation of APIs consumed by mobile devices
  \end{itemize}
  \emph{Environment : Java 7 (framework propriétaire), Jersey, Oracle}
}

\cventry{2009}{Supélec}{}{Rennes}{}{
  Port of Microsoft Windows' group policies to Unix.\newline{}
  250h project, design, implementation and delivery of a core-module and the \emph{motd} plugin. Released as a free software.\newline{}
  \emph{Environment : Python, OpenLDAP, SVN}
}

\section{Education}
\cvitem{2017}{Advanced Scrum training (Agilar) : coaching individuals, coaching teams, coaching organizations, continuous improvement}
\cvitem{2014}{M101J: MongoDB for Java Developers}
\cvitem{2007 -- 2009}{École Supérieure d'Électricité (Supélec), Gif-sur-Yvette campus. \newline{} Expertise in Secured Information Systems (Rennes, 35)}
\cvitem{2005 -- 2007}{École Nationale Supérieure d'Arts et Métiers (ENSAM), Angers}

\section{Events}
\cvitem{Dec. 2015}{API days}
\cvitem{Jun. 2015}{dotScale}
\cvitem{Apr. 2015}{Devoxx France (3 days)}
\cvitem{May 2014}{dotScale}
\cvitem{Apr. 2014}{Devoxx France (2 days)}
\cvitem{Dec. 2013}{dotJS}
\cvitem{Mar. 2013}{Devoxx France (3 days)}


\section{Skills}
\subsection{Computer}
\cvitem{Languages}{Java, Scala, Python, SQL, shell (Bash)}
\cvitem{Web}{HTML/XHTML, CSS}
\cvitem{Frameworks}{Guice, Jersey, Play, AngularJS, JQuery}
\cvitem{Tools}{Maven, Git, SVN, Jenkins, Sonar, Nexus, Artifactory, Docker}
\cvitem{DBMS}{Oracle, MySQL, PostgreSQL, SQL Server, MongoDB, Cassandra}
\cvitem{Application servers}{Jetty, Tomcat, Microsoft IIS}
\cvitem{OS}{Unix/Linux (Arch, Debian, CentOS), Windows}

\subsection{Languages}
\cvitem{English}{Upper intermediate level (TOEIC : 875)}
\cvitem{Spanish}{Elementary (read, written, basic listening/speaking)}

\section{Miscellaneous}
\cvitem{Blogging}{Almost-technical blog (\httplink[dericbourg.net]{http://www.dericbourg.net})}
\cvitem{Music}{\begin{itemize}
  \item Guitar (over 20 years)
  \item Playing in a band (15 years)
\end{itemize}}
\cvitem{Boating}{Boat licence (sea, river)}
\cvitem{Personnal commitment}{\begin{itemize}
  \item First-Aid Officer
  \item Non-violence
  \item NonViolent Communication
\end{itemize}}
\cvitem{Publication}{
  French translation of the book \emph{\href{https://github.com/adericbourg/coreprotocols-fr}{The Core Protocols: A Guide to Greatness}} by Richard Kasperowski (ISBN 978-1973931447)
}
\end{document}
